\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
%\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}


\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in


\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{0}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[3]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
      {\url{#2}}\\ \smallskip 
      {\href{mailto:#3}{#3}}\\ \smallskip
		\end{center}
	\end{changemargin}
}

\newcommand{\jobtitle}[3]{
	\textbf{#1}, \emph{#2} \hfill \emph{#3}\\
}

\newcommand{\jobdescription}[1]{
	\begin{changemargin}{0.15in}{0.15in}
    \smallskip
		{#1}
    \medskip
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
{\Large \textbf{Miguel A. Aparicio}} \\
(682)-329-2022 \\
\href{mailto:maparici@caltech.edu}{maparici@caltech.edu} \\
 Pasadena, California \\
 \begin{tabular}{l|l}
\href{https://www.linkedin.com/in/miguel-angel-aparicio-9a681a1a3/}{LinkedIn } & \href{https://github.com/jar0ch0}{ Github} 
\end{tabular}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\vspace{14pt}
	\textbf{California Institute of Technology} \hfill \emph{Present - June 2025} \\
	\emph{Bachelor of Science in Computer Science and Mathematics}\\
	
\end{body}

\medskip
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Skills}

%Spanish?
\begin{body}
	\vspace{14pt}
	\emph{\textbf{Programming:}}{} Java, HTML/CSS, JavaScript, Python, \LaTeX\\
	\medskip
	\emph{\textbf{Selected Technologies:}}{} Git, Linux\\
\end{body}

\medskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Experience}

\begin{body}
	\vspace{14pt}
%Google CSSI
  \jobtitle{Freshman Summer Research Institute}{Caltech}{August 2021 - September 2021}
  \jobdescription{
    The FSRI program consisted of four weeks of intensive math courses and a five weeks of summer research assignment. I was matched with a research mentor that allowed me to delve deeper into the inner-workings behind machine learning at-large, with some focus on neural networks. The program ended with a research presentation during which I explained to peers the work I had been conducting.
  }
%FSRI Research
	\jobtitle{CSSI Scholar}{Google}{June 2021 - August 2021}
  \jobdescription{
    Across four weeks, I engaged in an intensive computer science summer program for young, aspiring, high-achieving aspiring computer scientists. While connecting with like-minded peers and Google software developers, I completed a project-based JavaScript curriculum, focused on fundamentals, taught by Google engineers. During this same time, I attended product design, resume development, and software engineering interview workshops. The last week of the program, I developed a Chrome extension alongside a peer that facilitates the browsing of images on any website, accomplishing the finding and sorting of images as seen in the project by utilizing Javascript. In the end, alongside my partner I delivered a collaborative final project presentation that included a live demonstration to Google employees and community leaders.
  }

\end{body}

\medskip





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
\header{Awards and Honors}

\begin{body}
	\vspace{14pt}
	\textbf{National Hispanic Scholarship} \hfill{} \emph{2021}\\
	\medskip
	\textbf{Questbridge Match Scholarship} \hfill{} \emph{2020}\\
\end{body}

\medskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Leadership
\header{Activities}

\begin{body}
	\vspace{14pt}
	\textbf{Fixing Retro Videogame Consoles} \hfill {} \emph{2017 - Present}\\
	\jobdescription { }
\end{body}

\end{document}

